### 2020-03-27 Literature Review/Literature Review - Revised/sections/DynMARL.tex
Completed initial ParameterSweep

>>>>

    \section{Applications}

    The ability to predict learning is crucial towards understanding the behaviour of learning
    agents. It provides a qualitative understanding of the differences between algorithms and allows
    for a better understanding of the conditions under which each algorithm is appropriate, as well
    as how to choose parameters in such a way to achieve desired effects. It can be argued
    that the above methods presume some knowledge of the payoff matrices in order to generate these
    predictions. However, a re
